Something Something

### 2020-12-05 papers/SOSP21/draft.tex
Update paper notes

\begin{abstract}
\end{abstract}

@@

\section{Introduction}
\label{intro}
\section{Example \& Overview}
\label{overview}

>>>>

\begin{abstract}
This paper presents \sys, a system for parallelizing \unix shell scripts. 
To address performance and correctness concerns 
\sys introduces an ahead-of-time/just-in-time compilation hybrid to address key runtime challenges specific to the \unix shell---\eg parameter and variable expansion, command substitution, and word splitting.
A set of high-performance primitives such as a windowed \ttt{drain}er and token-based \ttt{split}ter offer further  performance and correctness improvements.
A resource-aware superoptimization component explores the trade-off space to identify configurations 
We evaluate \sys across a variety of hardware and software configurations using an extensive suite of more than 3K scripts including all 418 locale-independent tests from the POSIX suite.
% (1) all 418 locale-independent tests from the POSIX suite,
% (2) 112 scripts from the literature,
% (3) 
\sys's execution produces results that are correct with respect to sequential execution, significantly speeding up parallelizable scripts with sub-second elasticity characteristics. % important for interactive use.
\end{abstract}

@@

\section{Introduction}
\label{intro}

The \unix shell is an environment---often interactive---for composing scripts written in a plethora of programming languages.
This language-agnosticism, coupled with \unix's toolbox philosophy~\cite{mcilroy1978unix}, makes the shell the primary choice for specifying succinct and simple scripts for data processing, system orchestration, and other automation tasks.

\section{Example \& Overview}
\label{overview}
